VitalLens: Take A Vital Selfie

### 2023-12-07 paper.tex
Work on model evaluation

Vital Videos is a large, diverse dataset for rPPG collected in Belgium \cite{toye2023vital}.
It is the largest dataset we are aware of that is available for research without academic affiliation.
We use a slightly extended version of the medium instantiation (``VV-Medium''), which consists of 296 participants.
Both camera and participants are stationary in this dataset.

@@

The evaluation metrics include key vital signs such as heart rate and respiratory rate. We compare the performance of VitalLens with existing methods, including G, CHROM, POS, DeepPhys, and MTTS-CAN, using metrics such as Signal-to-Noise Ratio (SNR) and Mean Absolute Error (MAE).

@@

Table comparing G, CHROM, POS, DeepPhys, MTTS-CAN, VitalLens

>>>>

Vital Videos is a large, diverse dataset for rPPG collected in Belgium \cite{toye2023vital}.
It is the largest dataset we are aware of that is available for research without academic affiliation.
We use a slightly extended version of the medium instantiation (``VV-Medium''), which consists of 296 participants.
% TODO pull from data
Both camera and participants are stationary in this dataset.

@@

The evaluation metrics focus on the key vital signs, \textit{heart rate} and \textit{respiratory rate}.
We compare the performance of VitalLens with existing methods, including G, CHROM, POS, DeepPhys, and MTTS-CAN, using metrics such as Signal-to-Noise Ratio (SNR) and Mean Absolute Error (MAE).

We furthermore conduct a regression analysis using the chunk metadata to predict the performance of VitalLens.
This helps us identify the environmental factor affecting performance, and informs ``how to use'' advice offered to users of VitalLens.

@@

TODO evaluate for all methods

\begin{table}[h!]
 	\caption{Vitals estimation results on VV-Medium}
 	\label{tab:results-vv-medium}
 	\centering
  	\csvreader[
		tabular=lcccccc,
    	table head=\toprule Method & \multicolumn{1}{c}{Heart rate} & \multicolumn{2}{c}{Pulse wave} & \multicolumn{1}{c}{Respiratory rate} & \multicolumn{2}{c}{Respiration wave} \\ & MAE $\downarrow$ & SNR $\uparrow$ & $r \uparrow$ & MAE $\downarrow$ & SNR $\uparrow$ & $r \uparrow$ \\ \midrule,
    	table foot=\bottomrule,
    	late after line=\\,
    	before reading={\catcode`\%=12}, after reading={\catcode`\%=14}
  	]{data/results_vv_medium.csv}{}%
  {\csvcoli & \sisetup{round-mode=places,round-precision=2}\num{\csvcolii} & \sisetup{round-mode=places,round-precision=2}\num{\csvcoliii} & \sisetup{round-mode=places,round-precision=2}\num{\csvcoliv} & \sisetup{round-mode=places,round-precision=2}\num{\csvcolv} & \sisetup{round-mode=places,round-precision=2}\num{\csvcolvi} & \sisetup{round-mode=places,round-precision=2}\num{\csvcolvii} }
\end{table}

\begin{table}[h!]
 	\caption{Vitals estimation results on PROSIT test set}
 	\label{tab:results-prosit-test}
 	\centering
  	\csvreader[
		tabular=lcccccc,
    	table head=\toprule Method & \multicolumn{1}{c}{Heart rate} & \multicolumn{2}{c}{Pulse wave} & \multicolumn{1}{c}{Respiratory rate} & \multicolumn{2}{c}{Respiration wave} \\ & MAE $\downarrow$ & SNR $\uparrow$ & $r \uparrow$ & MAE $\downarrow$ & SNR $\uparrow$ & $r \uparrow$ \\ \midrule,
    	table foot=\bottomrule,
    	late after line=\\,
    	before reading={\catcode`\%=12}, after reading={\catcode`\%=14}
  	]{data/results_prosit_test.csv}{}%
  {\csvcoli & \sisetup{round-mode=places,round-precision=2}\num{\csvcolii} & \sisetup{round-mode=places,round-precision=2}\num{\csvcoliii} & \sisetup{round-mode=places,round-precision=2}\num{\csvcoliv} & \sisetup{round-mode=places,round-precision=2}\num{\csvcolv} & \sisetup{round-mode=places,round-precision=2}\num{\csvcolvi} & \sisetup{round-mode=places,round-precision=2}\num{\csvcolvii} }
\end{table}

\begin{table}[h!]
 	\caption{Vitals estimation results on VV-Ghana-Small test set}
 	\label{tab:results-vv-ghana-small-test}
 	\centering
  	\csvreader[
		tabular=lcccccc,
    	table head=\toprule Method & \multicolumn{1}{c}{Heart rate} & \multicolumn{2}{c}{Pulse wave} & \multicolumn{1}{c}{Respiratory rate} & \multicolumn{2}{c}{Respiration wave} \\ & MAE $\downarrow$ & SNR $\uparrow$ & $r \uparrow$ & MAE $\downarrow$ & SNR $\uparrow$ & $r \uparrow$ \\ \midrule,
    	table foot=\bottomrule,
    	late after line=\\,
    	before reading={\catcode`\%=12}, after reading={\catcode`\%=14}
  	]{data/results_vv_ghana_test.csv}{}%
  {\csvcoli & \sisetup{round-mode=places,round-precision=2}\num{\csvcolii} & \sisetup{round-mode=places,round-precision=2}\num{\csvcoliii} & \sisetup{round-mode=places,round-precision=2}\num{\csvcoliv} & \sisetup{round-mode=places,round-precision=2}\num{\csvcolv} & \sisetup{round-mode=places,round-precision=2}\num{\csvcolvi} & \sisetup{round-mode=places,round-precision=2}\num{\csvcolvii} }
\end{table}
